Objective-First Nanophotonic Design

### 2012-10-09 presentations/meta_book/Inverse_Methods.tex
Fixed typos in intro.

One of the strengths of this approach is that it recasts 
    the optimization problem into separably convex problems
    whose global optima can be reliably determined.  
Additionally, we show that our formulation is general enough 
    to encompasses the design of all linear nanophotonic structures 
    and is not limited to the design of optical metamaterials.
While this approach typically produces designs with very efficiencies 
    (typically 99/%)
    our solutions rely on continuously varying values of the dielectric constant 
    with respect to position across the optical structure being designed.  
Future approaches for dealing with this constraint are discussed 
    in Section \ref{sec:binary}.

>>>>

One of the strengths of this approach is that it recasts 
    the optimization problem into separably convex problems
    whose global optima can be reliably determined.  
Additionally, we show that our formulation is general enough 
    to encompass the design of all linear nanophotonic structures 
    and is not limited to the design of optical metamaterials.
While this approach typically produces designs with very high efficiencies 
    (typically 99\%)
    our solutions do feature continuously varying values of the 
    dielectric constant.
Future approaches for dealing with this constraint are discussed 
    in Section \ref{sec:binary}.
